A Large-Scale Study of the Use of Eval in R

### 2020-08-28 inst/paper/main.tex
Fix indentation
Add operation mix

\subsection{Operation Mix}

@@

>>>>

@@

\subsection{Operation Mix}
In this section, we look at the operations executed by the expressions and
symbols on evaluation. R is a lazy language, so symbols can be bound to promises
that can evaluate arbitrary code. All operations in R are function calls, even
primitive operations such as addition and assignment are treated as calls to
functions implemented in the interpreter. In our corpus, we observe 2.9G calls
to R functions of which 125.5M happen inside \eval. Furthermore, unlike
Javascript, R code also calls into peformant native implementations of numerical
and statistical routines. In the corpus there are 463.8M calls to native code of
which only 31.2M happens inside \eval.
Qualitatively, we observe all kinds of operations being executed inside \eval
calls, from numerical computing for statistical modeling to reflection and
metaprogramming for implementing DSLs. Even testing frameworks such \c{genthat}
heavily rely upon \eval to execute test code snippets. The core R implementation
is rife with uses of \eval for mundane things like accessing default values of
formal parameters and in statistical packages for computation.
